---
title: "This is a mockup certificate"
author: "M. Siple"
date: "6/28/2020"
output: 
  html_document:
    self_contained: yes
    css: corp-styles.css
    highlight: pygments
params:
  frequency: NA
  max_loudness: NA
  max_ping_dur: NA
  min_silent: NA
  name: NA
  devicename: NA
  characteristics: NA
---

<img src="NOAA_logo.svg" style="float:right;top:0px;right:0px;" height=100 />

<div class="watermark" align="center">CERTIFICATE</div>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#options(knitr.table.format = "html") 
library(tidyverse)
library(kableExtra)

frequency = params$frequency
max_loudness = params$max_loudness # also called "source level"
max_ping_dur = params$max_ping_dur
min_silent = params$min_silent
name = params$name
devicename = params$devicename
characteristics = params$characteristics

```

## Certificate of approval

INSERT NAME is approved to use the deterrent noted below according to the following specifications until [insert date one year from date of calculating/printing]. This deterrent is included under the National Guidelines for Non-lethally Deterring Marine Mammals.  INSERT NAME is not subject to the Marine Mammal Protection Act take prohibitions if the following deterrent is used in accordance with the below specifications.  



Deterrent name: INSERT DET NAME

Deterrent details: INSERT DETAILS

Expiration date: EXP DATE (one year + today's date)



Specifications entered:
```{r echo = FALSE}

  
x <- data.frame(Specification = c("Deterrent frequency (kHz)",
                                  "Source level (RMS SPL)",
                                  "Ping/pulse duration (seconds)",
                                  "Silent period between pings/pulses (seconds)"),
                Value = c(30,170,2,4))
x %>%
  kable(escape=FALSE) %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```