---
title: "Certificate of approval"
date: "6/28/2020"
output: 
  html_document:
    self_contained: yes
    highlight: pygments
params:
  frequency: NA
  max_loudness: NA
  max_ping_dur: NA
  min_silent: NA
  name: NA
  devicename: NA
  characteristics: NA
  isopleth.table: NA
  species.to.deter: NA
---

<!-- <img src="NOAA_logo.svg" style="position:absolute;top:0px;right:0px;" size= /> -->

```{r, echo=FALSE}
htmltools::img(src = knitr::image_uri(here::here("NOAA_logo.svg")),
               alt = 'logo',
               style = 'position:absolute; top:0; right:0; padding:10px; width: 100px')
```


<div class="watermark" align="center">CERTIFICATE</div>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
#options(knitr.table.format = "html") 
library(tidyverse)
library(kableExtra)

frequency = params$frequency
max_loudness = params$max_loudness # also called "source level"
max_ping_dur = params$max_ping_dur
min_silent = params$min_silent
name = params$name
devicename = params$devicename
characteristics = params$characteristics
expiration = Sys.Date() + 365
isopleth.table = params$isopleth.table
species.to.deter = params$species.to.deter
```


`r name` is approved to use the deterrent noted below according to the following specifications until `r expiration`. This deterrent is included under the National Guidelines for Non-lethally Deterring Marine Mammals. `r name` is not subject to the Marine Mammal Protection Act take prohibitions if the following deterrent is used in accordance with the below specifications.  



Deterrent name: `r devicename`

Deterrent details: `r characteristics`

Expiration date: `r expiration`

Species intended to be deterred by the device: `r species.to.deter`


## Specifications entered:
```{r echo = FALSE}

  
x <- data.frame(Specification = c("Deterrent frequency (kHz)",
                                  "Source level (RMS SPL)",
                                  "Ping/pulse duration (seconds)",
                                  "Silent period between pings/pulses (seconds)"),
                Value = c(30,170,2,4))
x %>%
  kable(escape=FALSE) %>% 
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```

## Compliance
```{r echo = FALSE}
y <- params$isopleth.table
y  %>%
  kable(escape=FALSE) %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed"))
```